### 2020-10-07 written/V1_model/V1_model.tex
latest writing for V1 section

\thispagestyle{plain}
\begin{center}                  % Center the following lines
{\Large Input/output properties of neuron-type population model of V1} \\
Sean Bittner \\
May 12, 2020 \\
\end{center}

\section{Introduction}
In section 3.3 of our bioRxiv preprint \cite{bittner2019interrogating}, we analyze the input/output properties of a 4 neuron-type model of V1.  
We identify degeneracies and sensitivities of neuron-type responses w.r.t specific inputs by visual inspection of the EPI distributions.  
In my opinion, these ``novel insights" are not particularly interesting.
Furthermore, these insights are easily obtained using an existing method -- approximate Bayesian computation (ABC).

In this write-up, I present a new line of inquiry in the same V1 circuit model as the paper.
Rather than conditioning on levels of increase of each neuron-type, we condition on the stabilization of each neuron-type.
EPI then presents us with a distribution of stimulation to this V1 circuit that does not change much a particular neuron-type response.

First, I show EPI converges to a distribution covering the set of samples produced by ABC.
This important sanity check, along with some ABC bias visualization, will make nice appendix figures.
Then, I show how EPI readily identifies the most efficacious patterns of stimulation.
Finally, we confirm two distinct mechanisms of E-population stabilization using EPI on the V1 model with inactivated populations.

\section{V1 model (same as bioRxiv post)}
We consider a four-dimensional circuit model with dynamical state given by the firing rate $x$ of each neuron-type population $x = \left[x_E, x_P , x_S, x_V \right]^\top$ (Fig. 1A). 
Given a time constant of $\tau = 20$ ms and a power $n = 2$, the dynamics are driven by the rectified and exponentiated sum of recurrent ($Wx$) and external $h$ inputs:

\begin{equation}
\tau \frac{dx}{dt} = -x + [W x+ h]_+^n.
\end{equation}

\begin{center}
\textbf{Figure 1: V1 model} \\
\includegraphics[scale=.4]{figs/V1_responses.pdf}
\end{center}

We considered fixed effective connectivity weights $W$ approximated from experimental recordings of publicly available datasets of mouse V1 \cite{allen2018layer, billeh2019systematic}.
The input $h = b + dh$ is comprised of a baseline input  $b = \left[ b_E, b_P , b_S , b_V \right]^\top = \left[ 1, 1, 1 ,1.25 \right]^\top$  and a differential input $dh = \left[ dh_E , dh_P , dh_S , dh_V\right]^\top$ to each neuron-type population.

We want to know the differential inputs $dh$ that maintain the steady state $x_{\alpha}$ for $\alpha \in \{E, P, S, V\}$. 
We see from Figure 1B that input to a single population in the recurrent circuit elicits a variety of responses across populations: E same, P up, S down, and V up.
We define the differential steady state $dx_{\alpha}$ as the change in steady state $x_{\alpha}$ when receiving input $h=b + dh$ with respect to the baseline $h = b$.
Maintaining the steady state of a neuron-type population amounts to the emergent property 
\begin{equation}
\mathcal{B}(\alpha, \sigma) ~~\triangleq~~ 
\mathbb{E} \begin{bmatrix} dx_{\alpha} \\ dx_{\alpha}^2 \end{bmatrix} ~~=~~ \begin{bmatrix} 0 \\ \sigma^2 \end{bmatrix}.
\end{equation}
In the following analyses, we chose $\sigma=0.25$.

\section{EPI agrees with ABC}
To get an idea of what distribution of parameters ($dh$) we should expect from EPI, we can use ABC to obtain a set of parameters related to the emergent property.  
We compare EPI to ABC with a rejection heuristic defined by the standard deviation of the differential responses $\sigma_{ABC}$
 \[f_{ABC}(dx_\alpha; \sigma_{ABC}) = |dx_\alpha| > 2\sigma_{ABC}.\]
 In other words, we ran ABC accepting parameters that generate differential responses within two standard deviations $\sigma_{ABC}=0.25$ of $dx_\alpha = 0$.
 In Figure 2, we see that the distributions obtained via EPI (colored by $\log q_\theta(z)$) are visually similar to those obtained via ABC (colored by $dx_\alpha$). \\

 \textbf{Figure 2}: EPI (left) vs ABC (right).  Arrows in EPI distribution indicate dimensions of maximal sensitivity at selected parameters $dh$. The importance of $v_S$ and $v_P$ are explained in section 4.2. \\
\begin{center}
$q_\theta(dh \mid \mathcal{B}(E,\sigma=0.25))$ \hspace{1.2in} $dh \sim ABC(E,\sigma_{ABC}=0.25)$. \\
\includegraphics[scale=0.25]{figs/V1_drdh_EPI_E.pdf} 
\includegraphics[scale=0.25]{figs/V1_drdh_ABC_E.png} \\
\clearpage
$q_\theta(dh \mid \mathcal{B}(P,\sigma=0.25))$ \hspace{1.2in} $dh \sim ABC(P,\sigma_{ABC}=0.25)$. \\
\includegraphics[scale=0.25]{figs/V1_drdh_EPI_P.png} 
\includegraphics[scale=0.25]{figs/V1_drdh_ABC_P.png} \\
$q_\theta(dh \mid \mathcal{B}(S,\sigma=0.25))$ \hspace{1.2in} $dh \sim ABC(S,\sigma_{ABC}=0.25)$. \\
\includegraphics[scale=0.25]{figs/V1_drdh_EPI_S.png} 
\includegraphics[scale=0.25]{figs/V1_drdh_ABC_S.png} \\
$q_\theta(dh \mid \mathcal{B}(V,\sigma=0.25))$ \hspace{1.2in} $dh \sim ABC(V,\sigma_{ABC}=0.25)$. \\
\includegraphics[scale=0.25]{figs/V1_drdh_EPI_V.png} 
\includegraphics[scale=0.25]{figs/V1_drdh_ABC_V.png} \\
\end{center}

There are some subtle differences between the EPI and ABC distributions, but some difference is to be expected.
Rather than simply attributing these differences to imperfection of the EPI optimization routine, we consider the the effect of bias in $dx_\alpha$ from ABC (and lack thereof from EPI).

When $\epsilon > 0$ in ABC, the samples are \textit{not} from the posterior distribution.
For $\epsilon > 0$, the ``posterior" predictive means of ABC $\mathbb{E}_{ABC(\alpha, \sigma_{ABC})}\left[dx_\alpha \right]$ may be far from zero.
In Figure 3, we see that with ABC, there is an increasingly negative bias in $\mathbb{E}_{ABC(\alpha, \sigma_{ABC})}\left[dx_\alpha \right]$ for greater error tolerances across all neuron-types.  
Additionally with ABC, there is no precise control of the variance $\mathbb{E}_{ABC(\alpha, \sigma_{ABC})}\left[dx_\alpha^2 \right]$, which may be undesireable.

In contrast, the first and second moments of $dx_\alpha$ are controlled to a specified degree of accuracy (Figure 4).
The variances of each distribution of $dx_\alpha$ are close to their target value $0.25^2 = 0.0625$ (see variances next to histograms of Figure 4). 
The regions of the ABC pairplots which have $|dx_\alpha| \approx 0.5$ are far less probable in the EPI distributions (by design), and can account for most mismatch observed.
As a note, there is a discontinuity in Figure 2, $EPI(E, \sigma=0.25)$ in the $dh_E$-$dh_S$ plane.
I'd like to see if I can run the optimization for more random seeds so that we obtain a more connected distribution.

\begin{center}
\textbf{Figure 3: Biased ABC} \\
\includegraphics[scale=0.4]{figs/V1_ABC_Tx.pdf}
\end{center}

\clearpage

\begin{center}
\textbf{Figure 4: Unbiased EPI} \\
\includegraphics[scale=0.4]{figs/V1_EPI_Tx.pdf}
\end{center}

\section{EPI-enabled analyses}
\subsection{Dimensions of sensitivity}
Each arrow in the EPI distributions (Fig. 2, left) points in the direction of maximal sensitivity indicated by the hessian $\partial^2 \log q_\theta(dh) / \partial dh \partial dh^\top$ evaluated at the $dh$ at the base of the arrow.
These patterns of input elicit a greater $dx_\alpha^2$ than (at least) 98.8\% of random stimulation patterns.
Each sensitivity vector is representative of a different stabilization mechanism.

\subsection{Confiriming distinct mechanisms of stabilization}
The sensitivity arrows on the EPI distribution for E-population stability (Fig. 2, top, left) indicate two distinct stability mechanisms for increased $dh_E$.
In one case, $dh_P$ must increase along with increased $dh_E$ (Fig. 2, top, left black arrow $v_P$).
In the other case, $dh_S$ must increase along with increased $dh_E$ (Fig. 2, top, left gray arrow $v_S$).
These inferred distributions and sensitivity vectors $v_P$ and $v_S$ motivate the following hypothesis:

H: If the P- and S-populations are inactivated, the only E-stabilization mechanism with increasing $dh_E$ will be that of the other population (S- or P-population, respectively) .

We can test this hypothesis with EPI, since it is optimized to identify the distribution of all inputs resulting in E-population stability.
We ran EPI with the same emergent property as Eq 2 ($\alpha=E$, $\sigma=0.25$) for two different inactivation scenarios.
In the P-inactivated case, we changed the baseline input to $b =b_{\not P} \triangleq \left[ 1, -5, 1 ,1.25 \right]^\top$, and to $b =b_{\not S} \triangleq \left[ 1, 1, -5 ,1.25 \right]^\top$ in the S-inactivated case.
To test for the existence of stabilization mechanisms corresponding to $v_P$ and $v_S$, we measured the most-sensitive dimension of the Hessian at all points in the inferred distribution.  
We declare that the P- or S-inactivated circuit lacks a stability mechanism, if no sensitivity vectors throughout the distribution are aligned with the corresponding sensitivity vector.

\begin{center}
\textbf{Figure 5}: Stability mechanisms of inactivated circuits.
\includegraphics[scale=.5]{figs/cos_dists.pdf}
\end{center}

Confirming our hypothesis, we found that only the $v_S$ stability mechanism is present in the P-inactivated circuit (Figure 5A), and that only the $v_P$ stability mechanism is present in the S-inactivated circuit (Figure 5B).
As expected, the samples of the inferred distributions aligned with the stability mechanism correspond to the sloped regions orthogonal to $v_S$ and $v_P$ (Figure 6).

\clearpage

\begin{center}
\textbf{Figure 6}: Inactivated circuit stability distributions.
\includegraphics[scale=.4]{figs/EPI_inactivation.pdf}
\end{center}

\section{Summary}
We have improved on our previous EPI analysis of V1 in the following ways:
\begin{enumerate}
\item We utilize a novel ability of EPI (Hessian evaluation).
\item Our scientific conclusion is about mechanisms of stability rather than high-level characteristics of responses.
\item We have validation of structure via ABC.
\item We characterize the issue of bias in ABC (and lack thereof in EPI).
\item The emergent property of ``neuron-type stabilization" follows the ethos of the definition of emergent property better than ``neuron-type population rate increase of $y$".
\end{enumerate}

I recommend substituting this work for section 3.3 in the bioRxiv manuscript. I'd be happy to write up a draft of such a section.

%\section{Isolated modulation paths using EPI}
%Let's say we want to find a stimulation pattern that changes the $\alpha$-population steady-state response $dx_\alpha$ as much as possible while keeping the rest the same.
%One can not simply stimulate the $\alpha$-population, since one must take into account the effects of the recurrent connectivity.
%Furthermore, such an input pattern producing isolated modulation may change nonlinearly.
%
%Beginning at $dh = \textbf{0}$, we seek a sequence of differential inputs that will increasingly change $dx_\alpha$, while maintaining $dx_\beta$, $\beta \in \{E, P, S, V\} \setminus	\{\alpha\}$.
%At each step in the path of inputs, the direction is selected to maximize change in $dx_\alpha$ and minimize change in $dx_{\beta \neq \alpha}$.
%These input selections can be guided by the EPI distributions $q_\theta(dh \mid \mathcal{B}(\alpha, 0.2))$ that result in the modulation of the $\alpha$ population within a given range.
%
%We leverage the availability of a functional representation of $\log q_\theta(dh \mid \mathcal{B}(\alpha, 0.2))$ to calculate the the hessians of the EPI distributions at each step of $dh$ in the path
%\begin{equation}
%\text{Hess}_\alpha(dh) = \frac{\partial^2 \log q_\theta(dh \mid \mathcal{B}(\alpha, 0.2))}{\partial dh \partial dh^\top}.
%\end{equation}
%
% We select the optimal direction of isolated modulation as vector v, which points in the maximally decreasing dimensions of $\log q_\theta(dh \mid \mathcal{B}(\alpha, 0.2))$, and minimally decreasing dimensions of $\log q_\theta(dh \mid \mathcal{B}(\beta, 0.2))$, $\beta \neq \alpha$:
% \begin{equation}
% v_\alpha^*(dh) = \argmin_v v^\top \text{Hess}_\alpha(dh) v - \sum_{\beta \neq \alpha} v^\top \text{Hess}_\beta(dh) v,
% \end{equation}
%  where $v\top v$ = 1.  $v_\alpha(dh)$ is obtained via an eigendecomposition:
%  \begin{equation}
%  v_\alpha^*(dh) = \argmin_v v^\top M_\alpha(dh) v
% \end{equation}
% \begin{equation}
%M_\alpha(dh) = \text{Hess}_\alpha(dh) - \sum_{\beta \neq \alpha} \text{Hess}_\beta(dh).
% \end{equation}
% The solution is the eigenvector with smallest eigenvalue of $M_\alpha(dh)$.
% 
% \includegraphics[scale=0.4]{figs/hess_paths.pdf}
%

>>>>

\thispagestyle{plain}
\begin{center}                  % Center the following lines
{\Large Draft of new V1 section} \\
Sean Bittner, Agostina Palmigiano \\
October 6, 2020 \\
\end{center}

\section{EPI clarifies the implications of contrast-response flipping on [noise quenching, inhibition stabilization] in V1}\label{results_V1}
Dynamical models of excitatory (E) and inhibitory (I) populations with supralinear input-output function have succeeded in explaining a host of experimentally documented phenomena.
In a regime characterized by inhibitory stabilization of strong recurrent excitation, these models give rise to paradoxical responses \cite{tsodyks1997paradoxical}, selective amplification  \cite{murphy2009balanced}, surround suppression \cite{ozeki2009inhibitory} and normalization \cite{rubin2015stabilized}. 
Despite their strong predictive power, E-I circuit models rely on the assumption that inhibition can be studied as an indivisible unit. 
However, experimental evidence shows that inhibition is composed of distinct elements -- parvalbumin (P), somatostatin (S), VIP (V) --
composing 80\% of GABAergic interneurons in V1 \cite{markram2004interneurons, rudy2011three, tremblay2016}, and that these inhibitory cell types follow specific connectivity patterns (Fig. \ref{fig:SV_flip}A) \cite{pfeffer2013inhibition}.
Recent theoretical advances \cite{litwin2016inhibitory, GarciaDelMolino2017, Chen2019},  have only started to address the consequences of this multiplicity in the dynamics of V1, strongly relying on linear theoretical tools. 
Here, we use EPI to analyze the posteriors of a stochastic nonlinear dynamical model of V1 conditioned on the emergent property of contrast-dependent S-V flipping.
We then [use this info to make a statement about ...]

Specifically, we consider a four-dimensional circuit model with dynamical state given by the firing rate $x$ of each neuron-type population $x = \left[x_E, x_P , x_S, x_V \right]^\top$. Given a time constant of $\tau = 20$ ms and a power $n = 2$, the dynamics are driven by the rectified and sum of recurrent inputs $Wx$, external inputs $h$, and external noise $\epsilon \sim \mathcal{N}(0, \sigma_{\epsilon}^2)$:

\begin{equation}
\tau \frac{dx}{dt} = -x + [W x+ h + \epsilon]_+^n.
\end{equation}

We considered fixed effective connectivity weights $W$ approximated from experimental recordings of publicly available datasets of mouse V1 \cite{allen2018layer, billeh2019systematic} (see Section \ref{methods_V1}).
The input $h = b + dh$ is comprised of a baseline input  $b = \left[ b_E, b_P , b_S , b_V \right]^\top$ and a differential input $dh = \left[ dh_E , dh_P , dh_S , dh_V\right]^\top$ to each neuron-type population.  
Throughout subsequent analyses, the baseline input is $b = \left[ 1 ,1,1,1\right]^\top$.

With this model, we are interested in the differential responses of each neuron-type population to changes in input $dh$. 
Initially, we studied the linearized response of the system to input $\frac{dx_{ss}}{dh}$ at the steady state response $x_{ss}$, i.e. a fixed point. 
All analyses of this model consider the steady state response, so we drop the notation $ss$ from here on.
While this linearization accurately predicts differential responses $dx = \left[ dx_{E} , dx_{P} , dx_{S} ,dx_{V} \right]^\top$  for small differential inputs to each population $dh = \left[ 0.1 , 0.1 , 0.1 , 0.1 \right]^\top$ (Fig \ref{fig:V1_EPI}B left), the linearization is a poor predictor in this nonlinear model more generally (Fig. \ref{fig:V1_EPI}B right).  
Currently available approaches to deriving the steady state response of the system are limited.

\clearpage
\begin{figure}[h]
\caption{\small \textbf{A}.  Four-population model of primary visual cortex with excitatory (black), parvalbumin (blue), somatostatin (red), and VIP (green) neurons.   Some neuron-types largely do not form synaptic projections to others  (excitatory and inhibitory projections filled and unfilled, respectively).
\textbf{B}. EPI posterior $q_\theta(z \mid \mathcal{B}_{S-V})$ for S-V flipping. The obtained posterior is visualized as 500 samples from the inferred distribution colored by $\log(q_\theta(z))$. This posterior is bimodal and concentrated in planes $dh_E > 0$ and $dh_E < 0$ at distinct modes $z_1$ (black star) and $z_2$ (gray, star), respectively.  Bottom-left: Posterior predictive distribution of the emergent property statistics with respect to the constrained means (black, dashed line) and variances (gray, dashed lines at two stds). 
\textbf{C}. Posterior predictive distribution of $d_{S-V}(h)$ of each mode shows that the $z_1$-mode produces V-to-S flipping with increasing contrast and the $z_2$-mode produces S-to-V flipping.
\textbf{D}. Model simulations at the mode $z_1$ at $b_1$ (left), $b_1 + dh_1^{(c)}$ (middle), and steady state solutions for varying levels of contrast (right).  Shaded area is one standard deviation according to randomness of $\epsilon$.  \textbf{E}. Same as D. for $z_2$. \textbf{F}. ...
 }\label{fig:SV_flip}
\begin{center}
\includegraphics[scale=.31]{figs/Fig3/Fig3.pdf}
\end{center}
\end{figure}
\clearpage

TODO Summarize S-V flipping phenomena and why it's a good EP
TODO Explain that we can't really fit the whole data-set of responses yet because the model is quite constrained.
TODO Motivate this input model, where $dh^{(c)}$ is the direction of increasing contrast.

\begin{equation}
 \begin{bmatrix} h_E \\ h_P \\ h_S \\ h_V \end{bmatrix} =  \begin{bmatrix} b_E \\ b_P \\ b_S \\ b_V \end{bmatrix} +  \begin{bmatrix} dh^{(c)}_E \\ dh^{(c)}_P \\ 0 \\ 0 \end{bmatrix} 
\end{equation}

Since we are unsure what either the baseline input $b$ and contrast-dependent change in input $dh^{(c)}$ should be, we treat them as free parameters when running EPI.
\begin{equation}
 z =  \begin{bmatrix} b_E & b_P & b_S & b_V & dh^{(c)}_E & dh^{(c)}_P \end{bmatrix}^\top
\end{equation}
We consider positive baseline inputs $b_\alpha \in \left[0, 3 \right]$ and small contrast-dependent changes in input $|dh_\alpha| \leq 1$.  
To find parameters resulting in S-V flipping, we focus on models driven by nominal amounts of external noise $\sigma_{\eta} = 0.1$.

We formulate the emergent property of S-V flipping with a statistic measuring he difference in steady state ($x_ss$) between the S- and V-population at a given input:
\begin{equation}
d_{S-V}(h) = x_{ss,S}(h) - x_{ss,V}(h).
\end{equation}
For S and V to flip their steady states, the difference between the S- and V-population rates at $h = b$ must have opposite sign from $h = b + dh$.  Therefore, we stipulate the emergent property of S-V flipping to require the product between $d_{S-V}(b)$ and $d_{S-V}(b+dh)$ to be appreciably negative.  Second we stipulate that the differences between S and V in each input condition cancel out on average ($d_{S-V}(b) + d_{S-V}(b+dh)$ is 0 on average).  The means and variances of the emergent property statistics were sensibly chosen based on some inexpensive model simulations within the parameter bounds.

\begin{equation}
\mathcal{B}_{S-V} \triangleq \mathbb{E}\begin{bmatrix} d_{S-V}(b)d_{S-V}(b+dh) \\ \left( d_{S-V}(b)d_{S-V}(b+dh) - (-0.25) \right)^2 \\  d_{S-V}(b) + d_{S-V}(b+dh) \\  \left( d_{S-V}(b) + d_{S-V}(b+dh)\right)^2 \end{bmatrix} = 
\begin{bmatrix} -0.25 \\ 0.125^2 \\ 0 \\ 0.125^2 \end{bmatrix}
\end{equation}

We ran EPI to inspect the structure of the posterior distribution of $z$ conditioned on S-V flipping shown in Fig 2.  
It is clear from this visualization that S-V flipping in this V1-model is sensitive with respect to some parameter settings and robust with respect to others.
Additionally, the posterior is bimodal: there is one mode in each of the hyperplanes $dh_E < 0$ and $dh_E > 0$.

The structure of the V1 model S-V flipping posterior yields the following insights:
\begin{enumerate}
\item The marginal distributions of $q_\theta(h_P \mid \mathcal{B}_{S-V})$ and  $q_\theta(dh_P \mid \mathcal{B}_{S-V})$ are approximately uniform along their allowed range.  
The approximate uniformity of the $P-population$ parameter marginal distributions shows that the P-population plays little role in S-V flipping. 
\item The pairwise marginal distribution of $q_\theta(h_S, h_V \mid \mathcal{B}_{S-V})$ shows strong correlation between these parameters.
The strong correlation between $h_S$ and $h_V$ in the posterior reveals that S-V flipping is sensitive with respect to the baseline inputs to the S- and V-populations.
\textbf{Augment this to show that multidim info from Hessian is useful.}
The Hessian provided by EPI at the modes indicates that coordinated increases of $h_S$ and $h_V$ by a ratio of $\frac{h_S}{h_V} = 0.701$ will preserve S-V flipping, while changes in an orthogonal dimension will disrupt it.

\item This distribution is multimodal.
\end{enumerate}

%\section{Stability analysis}
%The input $h = b + dh$ is comprised of a baseline input  $b = \left[ b_E, b_P , b_S , b_V \right]^\top = \left[ 1, 1, 1 ,1.25 \right]^\top$  and a differential input $dh = \left[ dh_E , dh_P , dh_S , dh_V\right]^\top$ to each neuron-type population.  
%
%We want to know the differential inputs $dh$ that maintain the steady state $x_{\alpha}$ for $\alpha \in \{E, P, S, V\}$. 
%We see from Figure 1B that input to a single population in the recurrent circuit elicits a variety of responses across populations: E same, P up, S down, and V up.
%We define the differential steady state $dx_{\alpha}$ as the change in steady state $x_{\alpha}$ when receiving input $h=b + dh$ with respect to the baseline $h = b$.
%Maintaining the steady state of a neuron-type population amounts to the emergent property 
%\begin{equation}
%\mathcal{B}(\alpha, \sigma) ~~\triangleq~~ 
%\mathbb{E} \begin{bmatrix} dx_{\alpha} \\ dx_{\alpha}^2 \end{bmatrix} ~~=~~ \begin{bmatrix} 0 \\ \sigma^2 \end{bmatrix}.\\
%\end{equation}
%In the following analyses, we chose $\sigma=0.25$.
%
%\section{EPI agrees with ABC}
%To get an idea of what distribution of parameters ($dh$) we should expect from EPI, we can use ABC to obtain a set of parameters related to the emergent property.  
%We compare EPI to ABC with a rejection heuristic defined by the standard deviation of the differential responses $\sigma_{ABC}$
% \[f_{ABC}(dx_\alpha; \sigma_{ABC}) = |dx_\alpha| > 2\sigma_{ABC}.\]
% In other words, we ran ABC accepting parameters that generate differential responses within two standard deviations $\sigma_{ABC}=0.25$ of $dx_\alpha = 0$.
% In Figure 2, we see that the distributions obtained via EPI (colored by $\log q_\theta(z)$) are visually similar to those obtained via ABC (colored by $dx_\alpha$). \\
% 
% \textbf{Figure 2}: EPI (left) vs ABC (right).  Arrows in EPI distribution indicate dimensions of maximal sensitivity at selected parameters $dh$. The importance of $v_S$ and $v_P$ are explained in section 4.2. \\
%
%There are some subtle differences between the EPI and ABC distributions, but some difference is to be expected.
%Rather than simply attributing these differences to imperfection of the EPI optimization routine, we consider the the effect of bias in $dx_\alpha$ from ABC (and lack thereof from EPI).
%
%When $\epsilon > 0$ in ABC, the samples are \textit{not} from the posterior distribution.
%For $\epsilon > 0$, the ``posterior" predictive means of ABC $\mathbb{E}_{ABC(\alpha, \sigma_{ABC})}\left[dx_\alpha \right]$ may be far from zero.
%In Figure 3, we see that with ABC, there is an increasingly negative bias in $\mathbb{E}_{ABC(\alpha, \sigma_{ABC})}\left[dx_\alpha \right]$ for greater error tolerances across all neuron-types.  
%Additionally with ABC, there is no precise control of the variance $\mathbb{E}_{ABC(\alpha, \sigma_{ABC})}\left[dx_\alpha^2 \right]$, which may be undesireable.
%
%In contrast, the first and second moments of $dx_\alpha$ are controlled to a specified degree of accuracy (Figure 4).
%The variances of each distribution of $dx_\alpha$ are close to their target value $0.25^2 = 0.0625$ (see variances next to histograms of Figure 4).

\section{V1 Supplemental section}\label{methods_V1}

We considered fixed effective connectivity weights $W$ approximated from experimental recordings of publicly available datasets of mouse V1.  Specifically, Billeh et al. \cite{billeh2019systematic} produce estimates of the synaptic strength (in mV)
\begin{equation}
M = \begin{bmatrix} 
0.36 & -0.48 & -0.31 & -0.28 \\
1.49 & -0.68 & -0.50 & -0.18 \\
0.86 & -0.42 & -0.15 & -0.32 \\
1.31 & -0.41 & -0.52 & -0.37 \end{bmatrix}
\end{equation}
and connection probability
\begin{equation}
C = \begin{bmatrix} 0.16 & 0.411 & 0.424 &  0.087 \\
0.395 & .451 & 0.857 & 0.02 \\
0.182 & 0.03 & 0.082 & 0.625 \\
0.105 & 0.22 & 0.77 & 0.028 \end{bmatrix}.
\end{equation}

Multiplying these connection probabilities and synaptic efficacies gives us an effective connectivity matrix:
\begin{equation}
W = C \odot M = \begin{bmatrix} 
0.0576 & -0.197 & -0.131 & -0.0244 \\
0.589 & -0.307 & -0.429 & -0.00360 \\
0.157 & -0.0126  & -0.0123 & -0.200 \\
0.138 & -0.0902 & -0.400 & -0.0104 \end{bmatrix}.
\end{equation}

\begin{figure}[h]
\caption{\small \textbf{A}. ...
 }\label{fig:drdh}
\begin{center}
\includegraphics[scale=.3]{figs/FigSabc/FigSabc.pdf}
\end{center}
\end{figure}

\begin{figure}[h]
\caption{\small \textbf{A}. ...
 }\label{fig:drdh}
\begin{center}
\includegraphics[scale=.12]{figs/FigSX/FigSX.pdf}
\end{center}
\end{figure}
